### 2016-02-05 docs/ms_communitySynchrony.Rmd
updates with new introduction structure

\textbf{Number of Tables and Figures}:  Tables;  Figures

@@

<!-- \setlength{\parindent}{5ex} -->
\setlength{\parindent}{5ex}

Introduction
------------
Asynchrony in population dynamics (also called compensatory dynamics) among interacting species is a key mechanism by which biodiversity can stabilize aggregate community or ecosystem function [@Ives2002; @Gonzalez2009; @Loreau2010; @Loreau2013].
Experimental work in grassland communities provides strong evidence for the stabilizing effect of asynchronous population dynamics [@Hector2010; @DeMazancourt2013a; @Gross2014; @Hautier2014], but identifying what drives species synchrony in natural communities remains a challenge [@Loreau2008a; @Gonzalez2009; @Loreau2013].
The challenge lies in partitioning community synchrony among three mechanistic drivers of population fluctuations: inter and intraspecific density-dependence, environmental stochasticity, and demographic stochastcity [@Loreau2008a].
Ideally, each mechanism would produce a unique signature on community dynamics and we could infer mechanism by comparing observed synchrony to some null expectation [e.g., @Houlahan2007].
Unfortunately, theoretical work suggests there is no null expectation of community synchrony and the drivers of synchrony interact in complex ways that preclude inference from observations alone [@Loreau2008a; @Loreau2013].

>>>>

\textbf{Number of Tables and Figures}:  2 Tables;  4 Figures

@@

\newpage{}
<!-- THIS HOW TO COMMENT-OUT -->
\setlength{\parindent}{5ex}

Introduction
------------
The relationship between species richness and ecosystem stability depends on species synchrony [@Gonzalez2009].
All else being equal, the stability of ecosystem function is highest when species dynamics are asynchronous [@DeMazancourt2013a].
Thus, a mechanistic understanding of the diversity-stability relationship requires understanding the processes that increase or decrease species synchrony in nature.
In the simplest case, when interspecific interactions and demographic stochasticity are weak, species synchrony is entirely determined by the synchrony of species' responses to fluctuating environmental conditions [@Loreau2008a; @Loreau2013].
Synchrony is highest when species' environmental responses are perfectly correlated, and declines as environmental responses diverge [@Ives2002; @Loreau2008a; @Loreau2013].
Alternatively, if environmental forcing is weak, interspecific competition can lead to compensatory dynamics that desynchronize species dynamics [@Lehman2000].
Of course, real communities are subject to some combination of environmental stochasticity, interspecific competition, and demographic stochasticity that complicate predictions from special theoretical cases [@Loreau2013].

The fact that species synchrony emerges from complex interactions among species' environmental responses, species interactions, and demographic stochasticity makes it difficult to disentangle the drivers of synchrony in observational data [e.g., @Houlahan2007].
Weak synchrony could reflect positive environmental correlations offset by strong competition, or weak environmental correlations and weak competition.
Likewise, demographic stochasticity can induce ecological drift in small populations that mask signals of competition and the environment [@Loreau2008a; @DeMazancourt2013a].
Therefore, inference on the processes that drive synchrony from metrics of synchrony, like summed community covariance, alone is prone to error.
@Mutshinda2009 attempted to overcome some of the limitations of inferring process from pattern by fitting a dynamic population model to several community time series of animal abundance.
They used a statistical technique to decompose temporal variation into competition and environmental components, and found that postively correlated environmental responses among species determined community dynamics.
However, Mutshinda et al.'s (2009) modeling technique relied on abundance data that may or may not reliably capture competitive interactions that occur at the individual level.

Here, we explicitly test theory on the drivers of species synchrony by parameterizing and simulating dynamic, multi-species population models fit to long term demographic data from five semi-arid grasslands [@Chu2015].
We use the fitted population models to simulate communities with and without interspecific interactions, environmental forcing, and demographic stochasticity.
Our modeling approach allows us to draw inference from real ecological systems that would otherwise be impossible using strictly statistical [e.g., @Mutshinda2009], experimental [e.g., @Gross2014], or observational [e.g., @Houlahan2007] approaches.
Given that our models capture the essential features of community dynamics important to synchrony (density-dependence, demographic and environmental stochasticity) and that these models are able to reproduce observed plant abundances [@Chu2015], perturbing the models reveals the processes responsible for the degree of species synchrony in our focal grassland communities.
Our main focus is on the synchrony of species' per capita growth rates since they represent a species immediate response to environmental conditions and competition.
However, we also analyze synchrony of plant cover (a metric of abundance) to relate our findings to previous research.

Our approach has several advantages.
First, we can use the models the directly compare synchrony from communities with and without different processes operating.
This means we do not have to rely on biased null expectations, such as independent species fluctuations, to determine if competition or environmental responses are more important -- we can test for this directly.
Second, our models represent natural communities, rather than experimentally-assembled communities.
This means our results may be more generalizable then results obtained from biodiversity-ecosystem function experiments where strong, but transient, competition is a hallmark [@Gross2014].
Third, our models are based on individual-level demographic data, which allows us to accurately estimate inter and intraspecific competition.
Lastly, we can use the models to estimate the synchrony of species' low density growth rates in the absence of interspecific competition.
Experimental analyses must rely on species' growth in monoculture as an indicator of a species' response to the environemnt, but low density growth rates are a direct measure of a species' immediate response to environmental conditions.
In combination, our dynamic modeling approach represents the most direct means toward unraveling the process that jointly determine community dynamics, species synchrony, and ultimately ecosystem stability.

<!-- COMMENT THIS OUT FOR NOW...

We follow the theory of @Loreau2008a, who show that in a neutral community of *S* species, expected synchrony ($\phi_r$) is defined as:

Asynchrony in population dynamics (also called compensatory dynamics) among interacting species is a key mechanism by which biodiversity can stabilize aggregate community or ecosystem function [@Ives2002; @Gonzalez2009; @Loreau2010; @Loreau2013].
Experimental work in grassland communities provides strong evidence for the stabilizing effect of asynchronous population dynamics [@Hector2010; @DeMazancourt2013a; @Gross2014; @Hautier2014], but identifying what drives species synchrony in natural communities remains a challenge [@Loreau2008a; @Gonzalez2009; @Loreau2013].
The challenge lies in partitioning community synchrony among three mechanistic drivers of population fluctuations: inter and intraspecific density-dependence, environmental stochasticity, and demographic stochastcity [@Loreau2008a].
Ideally, each mechanism would produce a unique signature on community dynamics and we could infer mechanism by comparing observed synchrony to some null expectation [e.g., @Houlahan2007].
Unfortunately, theoretical work suggests there is no null expectation of community synchrony and the drivers of synchrony interact in complex ways that preclude inference from observations alone [@Loreau2008a; @Loreau2013].
